LANGuage IDentification

### 2024-12-18 paper/paper.tex
start reviewing paper

%    Copyright (c)  2024  João Augusto Costa Branco Marado Torres.
%    Permission is granted to copy, distribute and/or modify this document
%    under the terms of the GNU Free Documentation License, Version 1.3
%    or any later version published by the Free Software Foundation;
%    with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts.
%    A copy of the license is included in the section entitled "GNU
%    Free Documentation License".
%
%    You should have received a copy of the GNU Free Documentation License
%    along with this program.  If not, see <https://www.gnu.org/licenses/>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Define Article %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Using Packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{empheq}
\usepackage{mdframed}
\usepackage{booktabs}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{color}
\usepackage{psfrag}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{bm}
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\selectlanguage{english}
\usepackage{blindtext}
\usepackage{csquotes}
\usepackage{hyperref}
\hypersetup{colorlinks,
           %citecolor=black,
           %filecolor=black,
           %linkcolor=black,
           %urlcolor=black,
           bookmarksopen=true}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\addbibresource{references.bib}
\usepackage{bookmark}
\usepackage{enumitem}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot[C]{\copyrightnotice}
\setlength{\headheight}{14.5pt}
%\addtolength{\topmargin}{-2.5pt}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,calc}
\usepackage{float}
\usepackage{wrapfig}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

    \section{License}
    \bigskip
    \begin{quote}
        \licensenotice
    \end{quote}
    \bigskip

@@

@@

    \begin{equation}
        \pd{E_{n}}{w_{ji}^{\nlayer}} & = \pd{E_{n}}{a_{j}^{\nlayer}} \pd{a_{j}^{\nlayer}}{w_{ji}^{\nlayer}}
    \end{equation}

@@

    \begin{equation}
        \pd{E}{w_{ji}^{\nlayer}} & = \displaystyle\sum_{n} \pd{E_{n}}{w_{ji}^{\nlayer}}
    \end{equation}

@@

    \printbibliography[
    heading=bibintoc
    ]

>>>>

%    Copyright (c)  2024  João Augusto Costa Branco Marado Torres.
%    Permission is granted to copy, distribute and/or modify this document
%    under the terms of the GNU Free Documentation License, Version 1.3
%    or any later version published by the Free Software Foundation;
%    with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts.
%    A copy of the license is included in the section entitled "GNU
%    Free Documentation License".
%
%    You should have received a copy of the GNU Free Documentation License
%    along with this program.  If not, see <https://www.gnu.org/licenses/>
%
%    <https://github.com/Marado-Programmer/langid>
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Define Article %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Using Packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{empheq}
\usepackage{mdframed}
\usepackage{booktabs}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{color}
\usepackage{psfrag}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{bm}
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\selectlanguage{english}
\usepackage{blindtext}
\usepackage{csquotes}
\usepackage{hyperref}
\hypersetup{colorlinks,
           %citecolor=black,
           %filecolor=black,
           %linkcolor=black,
           %urlcolor=black,
           bookmarksopen=true}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt,
defernumbers=true
]{biblatex}
\DeclareBibliographyCategory{cited}
\AtEveryCitekey{\addtocategory{cited}{\thefield{entrykey}}}
\addbibresource{references.bib}
\usepackage{bookmark}
\usepackage{enumitem}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot[C]{\copyrightnotice}
\setlength{\headheight}{14.5pt}
%\addtolength{\topmargin}{-2.5pt}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,calc}
\usepackage{float}
\usepackage{wrapfig}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\nocite{*}

@@

    \begin{abstract}
        This paper goes through the basics of supervised machine learning while
        simultaneously I implement with code what I'm learning without the use
        of libraries that hide what's really happening underneath and don't
        allow us to really understand and learn.

        I'm writing this paper because of school. But still, this is a topic I
        would like to really understand.

        Because now AI in general has become main stream it feels like that
        what already seemed like a black box for me, it has become even more
        abstracted away, so the average person can make use of these
        technologies.

        During my last internship (January to March 2023) there was a time I
        had to do some audio recognition stuff that I remember used
        \href{https://www.tensorflow.org/js}{tensorflow, the ML library for
        JavaScript}, under the hood.

        Good for me that there was an interface for the things I needed to
        implement, but if the guy that was giving me tasks had an idea in which
        those interfaces couldn't help, I would not know what to do.

        I know what I learned doing this project it's just the surface, but
        it's this foundation that I need to start learning more complex ideas.

        The project repository is available at: \\
        \url{https://github.com/Marado-Programmer/langid}
    \end{abstract}

    \section*{License}

    \bigskip
    \begin{quote}
        \licensenotice
    \end{quote}
    \bigskip

@@

    \section{Introduction}

    The initial goal was to create a model that would be trained on unlabeled
    phrases in different languages, and after that you would be able to prompt
    any phrase, and then it would tell which language was it written in.

    Turns out I didn't even get into unsupervised learning on this project. So
    the data is labeled.

    Still, I learned a lot and this paper will share some of the things I
    learned.

    Most things I learned/relearned (some things was talked about in class) by
    reading \cite{bishop} but when it comes to the backpropagation algorithm,
    if it wasn't for the playlist \cite{3b1b} I probably would still be stuck
    there.

@@

    \begin{equation}
        \pd{E_{n}}{w_{ji}^{\nlayer}} = \pd{E_{n}}{a_{j}^{\nlayer}} \pd{a_{j}^{\nlayer}}{w_{ji}^{\nlayer}}
    \end{equation}

@@

    \begin{equation}
        \pd{E}{w_{ji}^{\nlayer}} = \displaystyle\sum_{n} \pd{E_{n}}{w_{ji}^{\nlayer}}
    \end{equation}

    \section{Some Observations}

    I think the number of layers and total of neurons should grow when the
    input size grows too. If the input is two numbers and I want their
    multiplication as the output, 1 single neuron layer will not be able to do
    a great job.

    I also observed that the learning rate should decrease with the increase of
    layers/neurons or else the weights can become big numbers.

@@

    \printbibliography[
    heading=bibintoc,
    category=cited
    ]

    \printbibliography[
    heading=bibintoc,
    notcategory=cited,
    title={Other Resources}
    ]
